### 2020-04-01 ISSTA/implementation.tex
12 but tells more

While the formal definitions above offer a framework for checking nondeterminism, they leave unspecified the key notions of \emph{state},
\emph{visible state}, and \emph{actions}.  For example, we could
identify the state and visible state of a system as identical with the
full set of memory locations accessed by that system, and actions with
processor instructions.  However, this
definition is highly impractical.  First, it is
extremely inefficient to compare multiple executions for
full-memory-state equivalence at every instruction step.  Second, and
even more importantly, as noted in the introduction, very few programs
are deterministic in this strict sense.  What is a practical level of granularity for (visible) states and actions that
can be efficiently checked, and matches (for the most part) developer
and tester intuitions about what should behave deterministically?
Andrews et al. formalized a value-pool-based model \cite{AndrewsTR} that is widely used in
tools, including Randoop \cite{Pacheco}, where
unit tests are \emph{canonically} given as:

@@

We implemented our approach as a modification of the TSTL \cite{tstlsttt}
system, an open-source
language and tool for property-based testing
\cite{Hypothesis,ClaessenH00} of Python code.
%The TSTL {\tt examples} directory
%contains the SUTs needed to replicate our
%experiments.
\begin{comment}
TSTL can also be installed using Python's {\tt pip} tool, by typing
{\tt pip install tstl}; you will need to clone the github repository
to have access to the case studies used in the paper, however.

@@

In TSTL, a test consists of a sequence of
\emph{actions}, where actions execute arbitrary Python code, but are
expected to work by modifying the \emph{state} of a test, which is
stored in a fixed set of pools containing Python objects.  TSTL's
approach essentially follows the pool-based canonical form defined by
Andrews et al. and described above, but relaxes many of its restrictions
(e.g., a constant value can be used in a method call without first
assigning it to a pool). The
TSTL actions defined by a test harness correspond to the set $A$ of
actions in Section \ref{sec:formal}, and transitions 
result from executing action code, roughly, the array-canonical
statements.

>>>>

While the formal definitions above offer a framework for checking nondeterminism, they leave unspecified the key notions of \emph{state},
\emph{visible state}, and \emph{actions}.  For example, we could
identify the state and visible state of a system as identical with the
full set of memory locations accessed by that system, and actions with
processor instructions.  However, this
definition is highly impractical.  First, it is
extremely inefficient to compare multiple executions for
full-memory-state equivalence at every instruction step.  Second, and
even more importantly, as noted in the introduction, very few programs
are deterministic in this strict sense.  What is a practical level of granularity for (visible) states and actions that
can be efficiently checked, and matches developer
and tester intuitions about what should behave deterministically?
Andrews et al. formalized a value-pool-based model \cite{AndrewsTR} that is widely used in
tools, including Randoop \cite{Pacheco}, where
unit tests are \emph{canonically} given as:

@@

We implemented our approach as a modification of the TSTL \cite{tstlsttt}
system, an open-source
language and tool for property-based testing
\cite{Hypothesis,ClaessenH00} of Python code.  TSTL has
been used to detect (and usually fix) errors in a number of widely
used Python libraries, the Python implementation itself, the Solidity
compiler and a Solidity static analysis tool, and Mac OS.
 TSTL takes a harness (a
definition of \emph{what} to test, and what properties to check) and
generates tests using random testing and various other approaches.
TSTL is open source, and it and all examples used in this paper are
available at:  \url{https://github.com/agroce/tstl}.  We implemented
horizontal determinism checking (with both timing and process-based
differentiation of executions), failure determinism checking, and a
set of probabilistic delta-debugging strategies in TSTL, in order to
examine their effectiveness, and to make them available to users
performing Python library testing.
%The TSTL {\tt examples} directory
%contains the SUTs needed to replicate our
%experiments.
\begin{comment}
TSTL can also be installed using Python's {\tt pip} tool, by typing
{\tt pip install tstl}; you will need to clone the github repository
to have access to the case studies used in the paper, however.

@@

In TSTL, a test consists of a sequence of
\emph{actions}, where actions execute arbitrary Python code, but are
expected to work by modifying the \emph{state} of a test, which is
stored in a fixed set of pools containing Python objects.  TSTL's
approach essentially follows the pool-based canonical form defined by
Andrews et al. \cite{AndrewsTR} and described above, but relaxes many of its restrictions
(e.g., a constant value can be used in a method call without first
assigning it to a pool). The
TSTL actions defined by a test harness correspond to the set $A$ of
actions in Section \ref{sec:formal}, and transitions 
result from executing action code, roughly, the array-canonical
statements.
